### 2023-08-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny02
yny3

\section{Conclusions \label{sec:conclusion}}
In this work we used numerical simulations to examine the hydrodynamics of a multicomponent vesicle under strong confinement, which is a ubiquitous configuration in biology when a cell squeezes through a small channel. We refined the phase-field formulation in \citet{liu-mar-li-vee-low2017} with a new bending model that uses a sigmoidal function for the bending stiffness to retain positiveness in the bending modulus. The linear model \cite{liu-mar-li-vee-low2017} works well for a vesicle in free-space. However, under strong confinement we find it necessary to enforce the condition that the dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$  ($\beta = b_{\min}/b_{\max}$)  to avoid instability in membrane shapes (see \S~\ref{subsec:const_eq}). We focused on the hydrodynamics of a multicomponent vesicle in two types of confinement: a stenosis channel (\S~\ref{subsec:Stenosis}), and a contracting channel (\S~\ref{subsec:Contraction}). For both confining geometries we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.  The reason for focusing on

>>>>

\section{Conclusions \label{sec:conclusion}}
In this work we used numerical simulations to examine the hydrodynamics of a multicomponent vesicle under strong confinement, which is a ubiquitous configuration in biology when a cell squeezes through a small channel. We refined the phase-field formulation in \citet{liu-mar-li-vee-low2017} with a new bending model that uses a sigmoidal function for the bending stiffness to retain positiveness in the bending modulus. The linear model \cite{liu-mar-li-vee-low2017} works well for a vesicle in free-space. However, under strong confinement we find it necessary to enforce the condition that the dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$  ($\beta = b_{\min}/b_{\max}$)  to avoid instability in membrane shapes (see \S~\ref{subsec:const_eq}). We focused on the hydrodynamics of a multicomponent vesicle in two types of confinement: a stenosis channel (\S~\ref{subsec:Stenosis}), and a contracting channel (\S~\ref{subsec:Contraction}). For both confining geometries we varied the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and the initial distribution of lipid domains with a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.  The confinement ratio (defined as $2R_0/W$) in the stenosis is $1.67$, consequently the dependence of the vesicle shape on the capillary number is expected to be less sensitive according to results in \citet{aga-bir2020}. By fixing Peclet number at unity, we assume that the phase separation occurs at a much faster time scale than vesicle relaxation.

As a multicomponent vesicle enters/leaves a closely-fitted stenosis, coarsening of the lipid domains is expedited. However, strong confinement in the stenosis hinders the coarsening and the lipid domains remain separated as the vesicle moves through the stenosis. For a vesicle inside a stenosis, we define the lubrication layer and its corresponding width and examine the mechanical coupling between the boundaries in lipid domain and the planar shear flow inside the lubrication layer, which consists of a quadratic in height (due to pressure gradient in the thin film) and a linear shear term (due to membrane motion in the tangential direction). By analyzing these two contributions at various locations in the lubrication layer, we first identified that tank treading along the vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer width on the two sides.  We further elucidated  the correlation between the location of boundary between lipid domains, the Marangoni stress,  and the change of sign in the pressure gradient in the lubrication layer. These results may be useful to identify the lipid domains via the visualization of the flow in the lubrication layer.

For a multicomponent vesicle squeezing through a constriction, we found that front of the vesicle tends to be stiffer than the back of the vesicle.
